???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-28 article.tex
add ovo to methods.

with the tree structure is defined using left $I_L$ and right $I_R$ instance sets of nodes, with $I = I_L \cup I_R$. Instead of enumerating all possible tree structures, a greedy algorithm iteratively adds branches to the tree minimising $ \mathcal{L}_{split} $ in (\ref{eqn:enumerate}). The frequency of a variable's occurrence within a tree is directly attributed to the minimisation of the objective function (or loss) through the minimisation of  $ \mathcal{L}_{split} $.
\par
The frequency of a variable appearing as a node within the ensemble was used as a measure of importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function, translating the value into a simple count metric. Creating XGBoosted trees for each variable allowed the use of importance to show how strongly variables were associated with each other. The importance of predictor variables to economic variables was illustrated through the use of Sankey diagrams constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Other variable's interconnectedness was demonstrated through the use of a chord diagram also created using Holoviews.
\par
Each variable utilised 80\% of the data to train the XGBoost ensemble, with 20\% reserved for testing and validation. Testing was done through the iterative minimisation of the respective objective function for the variables type. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times.
 For  binary and multiclass variables data was split into 80\% training, 10\% testing and 10\% validation data. Due to class disparity in multiclass variables (most prominently in region) data was stratified into each subset at the same ratio of class occurrence. Validation was summarised through confusion matrices and their associated accuracy 
\par
The use of the XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyperparameters when selecting the final model. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables; with multiclass variables utilising the one verse the rest approach \citep{hanley1982meaning}.

>>>>

with the tree structure is defined using left $I_L$ and right $I_R$ instance sets of nodes, with $I = I_L \cup I_R$. Instead of enumerating all possible tree structures, a greedy algorithm iteratively adds branches to the tree minimising $ \mathcal{L}_{split} $ in (\ref{eqn:enumerate}). The frequency of a variable's occurrence within a tree is directly attributed to the minimisation of the objective function (or loss) through the minimisation of  $ \mathcal{L}_{split} $.
\par
The frequency of a variable appearing as a node within the ensemble was used as a measure of importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function, translating the value into a simple count metric. Creating XGBoosted trees for each variable allowed the use of importance to show how strongly variables were associated with each other. The importance of predictor variables to economic variables was illustrated through the use of Sankey diagrams constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Other variable's interconnectedness was demonstrated through the use of a chord diagram also created using Holoviews.
\par
Each variable utilised 80\% of the data to train the XGBoost ensemble, with 20\% reserved for testing and validation. Testing was done through the iterative minimisation of the respective objective function for the variables type. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times.
 For  binary and multiclass variables data was split into 80\% training, 10\% testing and 10\% validation data. Due to class disparity in multiclass variables (most prominently in region) data was stratified into each subset at the same ratio of class occurrence. Validation was summarised through confusion matrices and their associated accuracy 
\par
The use of the XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyperparameters when selecting the final model. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{hanley1982meaning}.
